---
title: "Using GitHub Project Boards"
author: "Harsh Baid"
vignette: >
  %\VignetteIndexEntry{projectboard}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(ghpm)
```

GHPM offers several useful functions for creating and grabbing data from project boards on GitHub. We can grab data general data from any project board by specifying a repository and then the project board number:

```{r}
str(get_projectboard_info("metrumresearchgroup", "pkgr", 1))
```

We can also grab information about the issues that are in each column in a project board
```{r}
get_projectboard("metrumresearchgroup", "pkgr")
```

The library also has ability to create project boards on the fly using the following command:
```{r, eval=FALSE}
create_projectboard("<Org Name>", "<Repo Name>", "<Project Board Title>", "<Project Board Body">)

# an optional field of columns can be specified to automatically create columns
create_projectboard("<Org Name>", "<Repo Name>", "<Project Board Title>", "<Project Board Body">, columns = c('First Column', 'Second Column', 'Third Column'))
```

Project boards can also be cloned using the command below. This is especially useful to quickly scaffold projectboards with automated workflows using a base repo as a template. The cloning process will only copy the name, body, columns, and workflows of a project board. It will NOT transfer over any issues or cards. This is currently limited to repos within in the same organization.

```{r, eval=FALSE}
clone_projectboard("<Org Name>", "<Repo to COPY FROM>", <Project Board Number>, "<Repo to COPY TO>")
```

